The French Covid-19 vaccination policy did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals

### 2022-07-04 ms/figs.Rmd
add table permutation results

# Save as csv
write.csv(tmp, file = "../ms/SuppTable_OR.csv", row.names = FALSE)
```

>>>>

# Save as csv
write.csv(tmp, file = "../ms/SuppTable_OR.csv", row.names = FALSE)

# Compute permutation values
qq <- 0.99 # quantile for the permutations
dates <- unique(outLR$thedate) # values of the dates
qperm <- rep(NA, length(dates)) # initialize output

for(idate in seq_along(dates)){
  thedate <- dates[idate]
  # Subset of the data for the permutation tests
  subT <- outLR[outLR$thedate == thedate & outLR$permutation == TRUE, ]
  # Compute quantile
  xq <- quantile(subT$OR.abs, probs = qq)
  qperm[idate] <- xq
}

tmp.perm <- data.frame(date = dates, q99 = qperm)
tmp.perm
